An interdisciplinary examination of stress and injury occurrence in athletes

### 2020-08-19 manuscript.Rmd
For submission

```{r include=FALSE}
options(scipen=999, digits = 2)
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
 source("r-files/functions.R")
 source("r-files/methods_code.R")
 source("r-files/results_code.R")

#load("all_data.RData")
#myEnv <- new.env()
#attach(myEnv, name="sourced_scripts")

@@

# Author Contributions

@@

@@

This paper adopts a novel, interdisciplinary approach to explore the relationship between 
psychosocial factors, physiological stress-related markers and occurrence of injury in athletes 
using a repeated measures design across a 2-year data collection period. At three data 
collection time-points, athletes completed measures of major life events, the reinforcement 
sensitivity theory personality questionnaire, muscle stiffness, heart rate variability and 
postural stability, and reported any injuries they had sustained since the last data collection. 
Two Bayesian networks were used to examine the relationships between variables and model 
the changes between data collection points in the study. Findings revealed muscle stiffness to 
have the strongest relationship with injury occurrence, with high levels of stiffness increasing 
the probability of sustaining an injury. Negative life events did not increase the probability 
of injury occurrence at any single time-point; however, when examining changes between 
time points, increases in negative life events did increase the probability of injury. In 
addition, the combination of increases in negative life events and muscle stiffness resulted in 
the greatest probability of sustaining an injury. Findings demonstrated the importance of 
both an interdisciplinary approach and a repeated measures design to furthering our
understanding of the relationship between stress-related markers and injury occurrence.

>>>>

```{r include=FALSE}
options(scipen=999, digits = 2)
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
 # source("r-files/functions.R")
 # source("r-files/methods_code.R")
 # source("r-files/results_code.R")
# 
load("all_data.RData")

#myEnv <- new.env()
#attach(myEnv, name="sourced_scripts")

@@

# Acknowledgements

@@

The content of this manuscript has been published as part of the thesis of Harry Fisher, @Fisher2019.

@@

### 2020-08-19 manuscript.tex
For submission

\hypertarget{author-contributions}{%
\section{Author Contributions}\label{author-contributions}}

@@

@@

\leavevmode\hypertarget{ref-Kuhn2008}{}%
78. Kuhn MC from JW, Weston S, Williams A, Keefer C, Engelhardt A. caret: Classification and Regression Training. \emph{Journal of Statistical Software} (2008) \textbf{28}: doi:\href{https://doi.org/10.1053/j.sodo.2009.03.002}{10.1053/j.sodo.2009.03.002}

@@

\leavevmode\hypertarget{ref-Ross2011}{}%
99. Ross SE, Linens SW, Wright CJ, Arnold BL. Balance assessments for predicting functional ankle instability and stable ankles. \emph{Gait and Posture} (2011) \textbf{34}:539--542. doi:\href{https://doi.org/10.1016/j.gaitpost.2011.07.011}{10.1016/j.gaitpost.2011.07.011}
\end{cslreferences}

>>>>

\hypertarget{acknowledgements}{%
\section{Acknowledgements}\label{acknowledgements}}

@@

The content of this manuscript has been published as part of the thesis of Harry Fisher, (100).

@@

\leavevmode\hypertarget{ref-Kuhn2008}{}%
78. Kuhn M. Building Predictive Models in R Using the caret Package. \emph{Journal of Statistical Software, Articles} (2008) \textbf{28}:1--26. doi:\href{https://doi.org/10.18637/jss.v028.i05}{10.18637/jss.v028.i05}

@@

\leavevmode\hypertarget{ref-Ross2011}{}%
99. Ross SE, Linens SW, Wright CJ, Arnold BL. Balance assessments for predicting functional ankle instability and stable ankles. \emph{Gait and Posture} (2011) \textbf{34}:539--542. doi:\href{https://doi.org/10.1016/j.gaitpost.2011.07.011}{10.1016/j.gaitpost.2011.07.011}

\leavevmode\hypertarget{ref-Fisher2019}{}%
100. Fisher H. An interdisciplinary examination of stress and injury occurence in athletes. (2019) Cardiff Metroploitan Univeristy, Cardiff. Available at: \url{https://repository.cardiffmet.ac.uk/handle/10369/11021}
\end{cslreferences}
